\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test with Stationary Time Series

### 2023-10-25 manuscript/manuscript.tex
Zoomed In Plots

>>>>

\subsection{Precipitation in Mansfield Connecticut}
Precipitation annual maximum in inches series data was retrieved from the 
National Oceanic and Atmospheric Administration.
\mc{https://hdsc.nws.noaa.gov/pfds/pfds_map_cont.html?bkmrk=ct}

\subsection{Microsoft Stock Returns}

\mc{https://www.nasdaq.com/market-activity/stocks/msft/historical}
